\begin{longtable}{>{\raggedright\arraybackslash}Xcc|cc|X|c}
\multicolumn{3}{c}{} & 
\multicolumn{2}{c}{\sffamily Requires} && 

\\*
\sffamily Name & 
\sffamily Type & 
\sffamily Mass / Rad &
\sffamily Reac. & \sffamily Gen. & 
\sffamily \centering Special &
\multirow{-2}{0.5cm}{\centering\sffamily Basic Mass}
\\*
\endfirsthead

\multicolumn{3}{c}{} & 
\multicolumn{2}{c}{\sffamily Requires} && 

\\*
\sffamily Name & 
\sffamily Type & 
\sffamily Mass / Rad &
\sffamily Reac. & \sffamily Gen. & 
\sffamily \centering Special &
\multirow{-2}{0.5cm}{\centering\sffamily Basic Mass}
\\*
\midrule
\endhead


\multicolumn{7}{r}{\footnotesize (continued next page) \faChevronCircleRight} 
\endfoot

\bottomrule
\endlastfoot

\midrule
\rowcolor{white}
Foamglass sintering & &
3 / 4 & 
& &
&
4
\\*
\rowcolor{lightgray}
Laser-heated pedestal growth &
\multirow{-2}{*}{\enhex{\sffamily \large{D}}} &
1 / 5 &
& \multirow{-2}{*}{\large{\encircle{e}}} &
\textbf{Superlens}: -1 to all colocated raygun prospecting rolls. &
3
\\

\midrule
\rowcolor{white}
Froth flotation & &
3 / 5 & 
& &
May only industrialize 4-hydration sites. &
4
\\*
\rowcolor{lightgray}
Femtochemistry &
\multirow{-2}{*}{\enhex{\sffamily \large{D}}} &
2 / 3 &
& &
\textbf{Mine Revival}: Industrialize a busted site of size ≥ 2 if decommission this card and 2 working robonauts. & 
2
\\

\midrule
\rowcolor{white}
CVD molding & &
3 / 5 & 
& &
&
3
\\
\rowcolor{lightgray}
Carbonyl Volatilization &
\multirow{-2}{*}{\enhex{\sffamily \large{M}}} &
2 / 5 &
& &
\textbf{Breeder \textsuperscript{232}Th enrichment}: If this card is on an S site, -3 to prospects there. & 
2
\\

\midrule
\rowcolor{white}
Electroforming & &
3 / 3 & 
& \encircle{e}&
&
4
\\*
\rowcolor{lightgray}
Impact mold sinter &
\multirow{-2}{*}{\enhex{\sffamily \large{M}}} &
3 / 5 &
& &
\textbf{Foamed Nickel}: If this card is on any site, -1 to prospecting rolls there. & 
3
\\

\midrule
\rowcolor{white}
Basalt fiber spinning & &
3 / 5 & 
(any) & &
&
4
\\*
\rowcolor{lightgray}
Von Neumann Santa Claus Machine &
\multirow{-2}{*}{\enhex{\sffamily \large{S}}} &
2 / 5 &
& &
\textbf{Divining Nubots}: A co-located crew, robonaut, or colonist is 1 less in ISRU. & 
2
\\

\midrule
\rowcolor{white}
Atomic layer deposition & &
2 / 2 & 
& \encircle{e}&
&
3
\\*
\rowcolor{lightgray}
Ilmenite semiconductor film &
\multirow{-2}{*}{\enhex{\sffamily \large{V}}} &
2 / 6 &
& &
\textbf{Power Girdle}: If used to industrialize a non-atmospheric site of size 8+, you don't need a generator and you gain the powersat faction privilege. & 
2
\\

\midrule
\rowcolor{white}
Carbo-chlorination & &
2 / 4 & 
& \encircle{e}&
&
3
\\*
\rowcolor{lightgray}
Solar carbotherm &
\multirow{-2}{*}{\enhex{\sffamily \large{V}}} &
2 / 5 &
& &
\textbf{Arcology}: if used to industrialize in the \Terra, \Venus, or \Mercury\space zones, you do not need to decommission a robonaut. & 
2
\\

\midrule
\rowcolor{white}
Fluidized-bed & &
3 / 4 & 
& &
&
4
\\*
\rowcolor{lightgray}
Atmospheric ISRU scoop &
\multirow{-2}{*}{\enhex{\sffamily \large{V}}} &
1 / 5 &
& \multirow{-2}{*}{\large{\encircle{e}}}&
\textbf{Scoop}: If operational, this card makes adjacent aerostat sites into 2-hydration and allows the atmospheric scooping refuel op. & 
3
\\

\midrule
\rowcolor{white}
ISRU Sabatier & &
3 / 4 & 
& \encircle{e}&
&
4
\\*
\rowcolor{lightgray}
Biophytolytic algae farm &
\multirow{-2}{*}{\enhex{\sffamily \large{V}}} &
3 / 5 &
& &
\textbf{Comet lichen}: If this card is on a D site, -2 to prospecting rolls there. & 
3
\\

\midrule
\rowcolor{white}
Magma electrolysis & &
3 / 3 & 
& \encircle{e}&
&
4
\\*
\rowcolor{lightgray}
Ionosphere lasing &
\multirow{-2}{*}{\enhex{\sffamily \large{V}}} &
2 / 6 &
& &
\textbf{Laser Powersat}: If used to industrialize an atmospheric site, you don't need a generator and you gain the \textbf{Powersat} faction privilege. & 
2
\\
\end{longtable}
